### 2019-09-09 manuscript/manuscript.tex

\begin{abstract}

  Natural selection can proceed in natural populations over short timescales,
  as evident from numerous studies demonstrating rapid phenotypic change.
  However, detecting these changes genome-wide is difficult, as rapid
  adaptation often proceeds from standing variation or is the result of
  polygenic selection, both of which leave faint genomic signals
  indistinguishable from a noisy background of genetic drift. As we developed
  in another paper \parencite{Buffalo2019-io}, one promising signal comes from
  the covariance between allele frequency changes observable from temporal
  genomic data, e.g. evolve-and-resequence studies. These temporal covariances
  reflect how the change in neutral allele frequency at one timepoint is
  predictive of the changes at later timepoints when there is heritable fitness
  variation in the population, as neutral alleles become stochastically linked
  with selected loci. Since genetic drift does not lead to temporal covariance,
  we can begin to directly estimate what fraction of the variation in allele
  frequency change through time is drift by linked selection. Here, we
  reanalyze two \emph{Drosophila simulans} evolve-and-resequence studies, and
  one artificial selection experiment in mice, to quantify the effects of
  linked selection over short timescales. Additionally, taking advantage of
  selection on replicated populations, we can directly estimate the covariance
  in allele frequency between replicates due to convergent selection pressure.
  Overall, we find that in the three studies we analyzed, linked selection has
  a remarkable impact on short term allele frequency dynamics that previously
  may have been attributed to genetic drift.

\end{abstract}

>>>>

\begin{abstract}
%Natural selection  as evident from numerous studies demonstrating
%rapid phenotypic change
  %As we developed
%  in another paper \parencite{Buffalo2019-io}, o
  \gc{Adaptation} can proceed in natural populations and \gc{selection
  experiments over} very short timescales.
  However, detecting these changes genome-wide is difficult, as rapid
  adaptation often proceeds from standing variation or is the result of
  polygenic selection, both of which \gc{may} leave faint genomic signals
  indistinguishable from a noisy background of genetic drift. One promising signal comes from
  the \gc{genome-wide} covariance between allele frequency changes observable from temporal
  genomic data, e.g. evolve-and-resequence studies. These temporal covariances
  reflect how the change in neutral allele frequency at one timepoint is
  predictive of the changes at later timepoints when there is heritable fitness
  variation in the population, as neutral alleles \gc{can remain
  associated with their random selected background over time.}
  %become stochastically linked
 % with selected loci.
  Since genetic drift does not lead to temporal covariance,
  we can \gc{use these covariances to} begin to directly estimate what fraction of the variation in allele
  frequency change through time is drift by linked selection. Here, we
  reanalyze two \emph{Drosophila simulans} evolve-and-resequence studies, and
  one artificial selection experiment in mice, to quantify the effects of
  linked selection over short timescales. Additionally, taking advantage of
  selection on replicated populations, we can directly estimate the covariance
  in allele frequency between replicates due to convergent selection
  pressure.
  \gc{We also identify signals of negative temporal covariance that
   show that selection reverses its direction for a reasonable
   proportion of loci over the time course of a selection experiment.}
  Overall, we find that in the three studies we analyzed, linked selection has
  a remarkable impact on short term allele frequency dynamics that previously
  may have been attributed to genetic drift
\end{abstract}
